Induced universal graphs for families of small graphs

### 2021-10-15 paper/paper.tex
A bit more writing

We note, first, that `degree' strategy appears to be at least as effective
as the `automorphisms' strategy for this instance, despite the lower
correlation observed in \Cref{fig:scatter}.  Perhaps most surprising is
that the `almost random' strategy performed better than any of the other
strategies.

@@

    \caption{TODO}
\label{fig:second-experiment}
\end{figure}

@@

    \caption{TODO}
\label{fig:second-experiment-using-sample}
\end{figure}

@@

>>>>

@@

    \caption{Using each of our four order strategies, we ran
        $\FuncSty{AllInducedUniversalGraphs}(\calF(5),9)$ 50 times. The figure
        shows the number calls to the subgraph isomorphism algorithm, in thousands.
        Horizontal lines show mean number of calls.}
\label{fig:second-experiment}
\end{figure}

We note, first, that `degree' strategy appears to be at least as effective
as the `automorphisms' strategy for this instance, despite the lower
correlation observed in \Cref{fig:scatter}.  Perhaps most surprising is
that the `almost random' strategy performed better than any of the other
strategies.
\Cref{tab:graphs-by-autom-count}

\input{img/graphs5}

@@

    \caption{Using each of our four order strategies, we ran
        $\FuncSty{AllInducedUniversalGraphs}(\calF,9)$ 50 times, where
        $\calF$ is a random subset of $\calF(5)$ containing 17 graphs. The figure
        shows the number calls to the subgraph isomorphism algorithm, in thousands.
        Horizontal lines show mean number of calls.}
\label{fig:second-experiment-using-sample}
\end{figure}

@@

\begin{figure}[htb]
    \centering
      \begin{tikzpicture}[>=latex',line join=bevel,scale=.4]
        \tikzstyle{every node}=[draw, circle, inner sep=1pt, minimum size=.1cm]
      \end{tikzpicture}
\label{fig:heuristic-regions}
\end{figure}
